Trajectories

### 2021-09-15 Rmd/report.Rmd
Add GitHub dark theme

---
title: "Trajectories"
output:
  github_document:
    pandoc_args: --webtex
bibliography: "trajectories.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = TRUE,
  echo = TRUE,
  warning = TRUE,
  dev.args = list(png = list(type = "cairo")),
  include = TRUE,
  out.width = "100%",
  results = "asis",
  dpi = 300
)
options(
  knitr.kable.NA = "-",
  knitr.duplicate.label = "allow",
  ggplot2.discrete.fill = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.discrete.colour = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.continuous.fill = ggplot2::scale_color_gradient,
  ggplot2.continuous.colour = ggplot2::scale_color_gradient
)

@@

# set params
tar_load_globals()
theme_set(theme_custom())

>>>>

---
title: "Trajectories"
output:
  html_document: default
  github_document:
    pandoc_args: --webtex
bibliography: "trajectories.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = TRUE,
  echo = FALSE,
  warning = TRUE,
  dev.args = list(png = list(type = "cairo")),
  include = TRUE,
  out.width = "100%",
  results = "asis",
  dpi = 300
)
options(
  knitr.kable.NA = "-",
  knitr.duplicate.label = "allow",
  ggplot2.discrete.fill = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.discrete.colour = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.continuous.fill = ggplot2::scale_color_gradient,
  ggplot2.continuous.colour = ggplot2::scale_color_gradient
)

@@

# set params
tar_load_globals()
theme_set(theme_github())
